\begin{thebibliography}{1}

\bibitem{wavelet}
M. M. Deshpande, J. G. Rana, and M. M. Pawar. \emph{"Human detection based on discrete Wavelet transform"}. Sustainable Energy and Intelligent Systems. IET Chennai International Conference. 3rd 2012.
\bibitem{hog}
N. Dalal and  B. Triggs. \emph{"Histograms of Oriented Gradients for Human Detection"}. Sustainable Energy and Intelligent Systems, IET Chennai International Conference, 3rd 2012.
\bibitem{rcnn}
Ross Girshick, Jeff Donahue, Trevor Darrell, and Jitendra Malik. \emph{"Region-based Convolutional Networks for Accurate Object Detection and Segmentation"}. IEEE Transactions on Pattern Analysis and Machine Intelligence, Volume 38.
\bibitem{slidingwin1} 
H. A. Rowley, S. Baluja, and T. Kanade. \emph{"Neural network-based face detection"}. TPAMI, 1998.
\bibitem{slidingwin2}
R. Vaillant, C. Monrocq, and Y. LeCun. \emph{"Original approach for the localisation of objects in images"}. IEE Proc on Vision, Image, and
Signal Processing, 1994.
\bibitem{slidingwin3}
Kevin Murphy, Antonio Torralba, Daniel Eaton, and William Freeman. \emph{"Object detection and localization using local and global features"}. Volume 4170 of the series Lecture Notes in Computer Science pp 382-400.
\bibitem{slidingwin4}
Anuj Mohan, Constantine Papageorgiou, and Tomaso Poggio. \emph{"Example-based object detection in images by components"}. IEEE Transactions on Pattern Analysis and Machine Intelligence, 23(4):349–361, 2001.
\bibitem{localinterestpoint1}
G. Bouchard and B. Triggs. \emph{"A hierarchical part-based model for visual object categorization"}. In CVPR, 2005.
\bibitem{slidingwin5}
Shaoqing Ren, Kaiming He, Ross Girshick, and Jian Sun. \emph{Faster R-CNN: Towards Real-Time Object	Detection with Region Proposal Networks}. Neural Information Processing Systems 2015.
\end{thebibliography}